New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2022-08-24 paper/paper.Rmd
revised abstract

---
title: |
  New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions
type: Short Technical Note
author:
  - name: Ursula Laa
    affil: a
    email: ursula.laa@boku.ac.at
  - name: Alex Aumann
    affil: b
    email: aaum0002@student.monash.edu
  - name: Dianne Cook
    affil: c
    email: dicook@monash.edu
  - name: German Valencia
    affil: b
    email: german.valencia@monash.edu
affiliation:
  - num: a
    address: |
      Institute of Statistics, University of Natural Resources and Life Sciences, Vienna
  - num: b
    address: |
      School of Physics and Astronomy, Monash University
  - num: c
    address: |
      Department of Econometrics and Business Statistics, Monash University
bibliography: biblio.bib
geometry: margin=2.5cm
abstract: | 
  We implement a new version of a manual tour that takes advantage of existing features in Mathematica to construct functions that interact with the position of the cursor. We demonstrate the usefulness of this new tool with an example exploring region boundaries in classification problems.
keywords: |
  data visualisation; grand tour; statistical computing; statistical graphics; multivariate data; dynamic graphics
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage{setspace}
  \usepackage{graphicx}
  \usepackage{nicematrix}
  \NiceMatrixOptions{code-for-first-row = \color{red} ,code-for-last-row = \color{red} ,code-for-first-col = \color{blue} ,code-for-last-col = \color{blue}}
output: rticles::tf_article
keep_tex: true
---

>>>>

---
title: |
  New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions
type: Short Technical Note
author:
  - name: Ursula Laa
    affil: a
    email: ursula.laa@boku.ac.at
  - name: Alex Aumann
    affil: b
    email: aaum0002@student.monash.edu
  - name: Dianne Cook
    affil: c
    email: dicook@monash.edu
  - name: German Valencia
    affil: b
    email: german.valencia@monash.edu
affiliation:
  - num: a
    address: |
      Institute of Statistics, University of Natural Resources and Life Sciences, Vienna
  - num: b
    address: |
      School of Physics and Astronomy, Monash University
  - num: c
    address: |
      Department of Econometrics and Business Statistics, Monash University
bibliography: biblio.bib
geometry: margin=2.5cm
abstract: | 
  This paper describes new user controls for examining high-dimensional data using low-dimensional linear projections and slices. A user can interactively change the coefficients of a variable in a low-dimensional projection, which is useful for exploring the sensitivity of structure to particular variables. The user can also interactively shift the slice center, which is useful for exploring how structure changes in local subspaces. These controls are implemented in Mathematica to take advantage of it's mathematics functions, and interactivity tools that allow construction of functions that interact with the position of the cursor. We demonstrate the usefulness of this new tool with an example exploring region boundaries in classification problems.
keywords: |
  data visualisation; grand tour; statistical computing; statistical graphics; multivariate data; dynamic graphics
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage{setspace}
  \usepackage{graphicx}
  \usepackage{nicematrix}
  \NiceMatrixOptions{code-for-first-row = \color{red} ,code-for-last-row = \color{red} ,code-for-first-col = \color{blue} ,code-for-last-col = \color{blue}}
output: rticles::tf_article
keep_tex: true
---

### 2022-08-24 paper/paper.tex
revised abstract

\begin{abstract}
We implement a new version of a manual tour that takes advantage of
existing features in Mathematica to construct functions that interact
with the position of the cursor. We demonstrate the usefulness of this
new tool with an example exploring region boundaries in classification
problems.
\end{abstract}

>>>>

\begin{abstract}
This paper describes new user controls for examining high-dimensional
data using low-dimensional linear projections and slices. A user can
interactively change the coefficients of a variable in a low-dimensional
projection, which is useful for exploring the sensitivity of structure
to particular variables. The user can also interactively shift the slice
center, which is useful for exploring how structure changes in local
subspaces. These controls are implemented in Mathematica to take
advantage of it's mathematics functions, and interactivity tools that
allow construction of functions that interact with the position of the
cursor. We demonstrate the usefulness of this new tool with an example
exploring region boundaries in classification problems.
\end{abstract}
